Accelerated Magnetic Resonance Imaging by Generative Adversarial Neural Networks

### 2018-02-19 paper.tex
Update title

\title{Accelerated Magnetic Resonance Imaging by Adversarial Neural Network}

@@

We introduce a practical, software-only framework, based on deep learning, for accelerating MRI acquisition, while maintaining anatomically meaningful imaging. This is accomplished by partial MRI sampling, while using an adversarial neural network to directly estimate the missing k-space samples. The inter-play between the generator and the discriminator networks enables the introduction of an adversarial cost in addition to fidelity loss used for optimizing the peak signal-to-noise ratio (PSNR). Promising image reconstruction results are obtained for 3T and 1.5T brain MRI, from a large publicly available dataset, where only 40\%, 25\%, and 16.6\% of the raw samples of each scan are used. To assess the clinical usability of the reconstructed images we also performed tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
Segmentation compatibility, measured in terms of Dice scores and Hausdorff distances, demonstrate the quality of the proposed MRI reconstruction with respect to other methods, including the widely-used Compressed Sensing.

@@

\subsection{PSNR and SSIM}
PSNR and SSIM are the most commonly used measures for evaluation of image reconstruction quality. PSNR measures the Mean Squared Error (MSE) between the fully-sampled MR image and the reconstructed image.
Quantitative evaluation is presented in~Table~\ref{tbl:PSNR_NO_MASK} and a graphical visualization in ~Figure~\ref{fig:error_psnr_errorbar}. The PSNR is calculated for the entire image without masking. Note that the proposed method outperforms the others. To support this, we also calculated the two-sample t-Test for the table's scores. The differences are statistically significant (p-values~$<0.005$) for all pairwise comparisons between the results of our method and the others.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\linewidth]{include/grp2/error_psnr_errorbar}
\caption{PSNR without masking error-bar}
\end{figure}\label{fig:error_psnr_errorbar}

>>>>

\title{Accelerated Magnetic Resonance Imaging by Generative Adversarial Neural Networks}

@@

We introduce a practical, software-only framework, based on deep learning, for accelerating MRI acquisition, while maintaining anatomically meaningful imaging. This is accomplished by partial MRI sampling, while using an generative adversarial neural network to directly estimate the missing k-space samples. The inter-play between the generator and the discriminator networks enables the introduction of an adversarial cost in addition to fidelity loss used for optimizing the peak signal-to-noise ratio (PSNR). Promising image reconstruction results are obtained for 3T and 1.5T brain MRI, from a large publicly available dataset, where only 40\%, 25\%, and 16.6\% of the raw samples of each scan are used. To assess the clinical usability of the reconstructed images we also performed tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
Segmentation compatibility, measured in terms of Dice scores and Hausdorff distances, demonstrate the quality of the proposed MRI reconstruction with respect to other methods, including the widely-used Compressed Sensing.

@@

\subsection{PSNR and SSIM}
PSNR and SSIM are the most commonly used measures for evaluation of image reconstruction quality. PSNR measures the Mean Squared Error (MSE) between the fully-sampled MR image and the reconstructed image.
Quantitative evaluation is presented in~Table~\ref{tbl:PSNR_NO_MASK} and a graphical visualization in~Figure~\ref{fig:error_psnr_errorbar}. The PSNR is calculated for the entire image without masking. Note that the proposed method outperforms the others. To support this, we also calculated the two-sample t-Test for the table's scores. The differences are statistically significant (p-values~$<0.005$) for all pairwise comparisons between the results of our method and the others.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\linewidth]{include/grp2/error_psnr_errorbar}
\caption{PSNR without masking error-bar}
\label{fig:error_psnr_errorbar}
\end{figure}
